---
title: "Bellabeat Case Study"
author: "Brian Wu"
date: "7/29/2021"
output: 
    html_document:
    theme: cosmo
    toc: yes
    toc_float: yes
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Introduction

![[Image Source](https://images.app.goo.gl/FZuNYQT7AZ9PZmDm7)](bellabeat_logo.jpg)

$~$

[Bellabeat](https://bellabeat.com/) is a tech-driven wellness company founded in 2013 by Sandro Mur and Urška Sršen. Bellabeat specializes in health-focused smart products for women and offer a line of products that help empower users with knowledge about their own health and habits. These products include:

- **Bellabeat App:** Provides users with a hub to track their health data related to their habits and activities.

- **Leaf:** Wellness tracker that can be worn as a bracelet, necklace, or clip that tracks activity, sleep, and stress. Connects to the Bellabeat app to provide the user insights into their daily wellness.

- **Time:** A watch that tracks user activity, sleep, and stress. Connects to the Bellabeat app to provide the user insights into their daily wellness.

- **Spring:** A water bottle that tracks daily water intake. Connects to the Bellabeat app to provide the user insights into their daily wellness.

- **Membership:** Gives users 24/7 access to fully personalized guidance based on their lifestyle and goals.

$~$

## Objective

Using data gathered from non-Bellabeat smart devices, we will try to identify trends in smart device usage and how those trends can help influence Bellabeat's marketing strategy.

$~$

## The Data

The data used in this analysis is from [Kaggle](https://www.kaggle.com/arashnic/fitbit) and was made available by the user [Möbius](https://www.kaggle.com/arashnic). These datasets were generated by respondents to a distributed survey via Amazon Mechanical Turk. 30 eligible Fitbit users consented to the submission of personal tracker data, including minute-level output for physical activity, heart rate, and sleep monitoring.

Upon initial examination of the 18 datasets, we immediately notice a few things:

- Data was collected between 3/12/2016 and 5/12/2016. 
- Datasets have differing levels of granularity, with some datasets containing minute-to-minute data and others containing daily data. 
- There does not appear to be any data regarding water intake.

We will keep these observations in mind as we delve deeper into the data.

$~$

## Data Prep

Let's start by load the necessary libraries:
```{r warning=FALSE, message = FALSE}
library(tidyverse)
library(lubridate)
library(janitor)
```


Importing the datasets
```{r}
daily_activity <- read_csv("dailyActivity_merged.csv")
daily_sleep <- read_csv("sleepDay_merged.csv")

```

```{r}

```

```{r}

```

```{r}

```


## Conclusions


